### 2014-10-28 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Update acknowledgments

The authors would like to thank XXXX. The authors would also like to thank John Culbertson, Director of the Montana Fire Services Training School, for his assistance in compiling Table~\ref{tab:LODD}. Finally, the authors would like to thank Joseph Willi of the University of Illinois Urbana-Champaign for his assistance in creating dimensioned drawings of the structure.

>>>>

The authors would like to thank Chief of Department Joanne Hayes-White, Battalion Chief Jose L. Velo, and Assistant Chief David L. Franklin of the San Francisco Fire Department for their assistance with this study and their dedication to improving firefighter safety. The authors would also like to thank John Culbertson, Director of the Montana Fire Services Training School, for his assistance in researching and compiling the flow path related LODD/LODI incidents shown in Table~\ref{tab:LODD}. Thanks to the NIOSH Fire Fighter Fatality Investigation and Prevention Program for their cooperation. Finally, the authors would like to thank Joseph Willi of the University of Illinois Urbana-Champaign for his assistance in creating dimensioned drawings of the structure.
